R Notebook

### 2022-02-11 Code/Simulation.Rmd
Add noisy function, test for KSgeneral

# Create the histograms displaying p-values from each test
hist1 <- suppressWarnings(test_rounded(10000, 100, 4))
hist2 <- suppressWarnings(test_rounded(10000, 100, 3))
hist3 <- suppressWarnings(test_rounded(10000, 100, 2))
hist4 <- suppressWarnings(test_rounded(10000, 100, 1))

# Create a master data_frame with all the results
histogram <- c(rep(".0001", 10000), rep(".001", 10000), rep(".01", 10000), rep(".1", 10000))
p_values <- c(hist1, hist2, hist3, hist4)
results <- data_frame(p_values, histogram)

# Generate histograms plot
hist_rounded <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value") + facet_wrap(.~histogram, scales = "free_y")
```

      # Generate random correlated data, perform a KS-test, and store the p-value
      data <- arima.sim(model = list(ar = ars[i]), rand.gen = rnorm, sd = sqrt(1-ars[i]^2), n = 100)
      ar_results <- add_row(ar_results, p_value = ks.test(data, "pnorm")$p.value, ar = ars[i])
    }
  }

 # Set AR coefficients and generate results
ars <- seq(-0.5, 0.5, by = 0.1)
ar_results <- suppressWarnings(test_correlation(1000, ars))

# Generate histograms plot
hist_correlation <- ggplot(ar_results, aes(x = p_value)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~ar, scales = "free_y", ncol = 3)
```

  results1 <- c()
  results2 <- c()
  results3 <- c()

    if (i%%100 == 0) {
      cat(i, " ")
    }

    # Generate random rounded data, perform 3 KS-tests, and store the p-values
    # 1. Using the rounded normal step function
    # 2. Using the naive continuous standard normal function
    data <- round(rnorm(n_samples), digits)
    results1[i] <- ks.test(data, sfun)$p.value
    results2[i] <- ks.test(data, "pnorm")$p.value
  }

# Create the histograms displaying p-values from each test
test1 <- suppressWarnings(test_dgof(10000, 100, 3))
test2 <- suppressWarnings(test_dgof(10000, 100, 2))
test3 <- suppressWarnings(test_dgof(10000, 100, 1))
results <- rbind(test1, test2, test3)

# Generate histograms plot
hist_dgof <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~test+digits, ncol = 3, scales = "free_y")
hist_dgof
```

    # Generate random rounded data, perform 2 KS-tests, and store the p-values
    # 1. Using the rounded normal step function
    # 2. Using the rounded normal step function with simulated p-values
    test <- round(rnorm(n_samples), digits)
    results1[i] <- ks.test(test, sfun)$p.value
    results2[i] <- ks.test(test, sfun, simulate.p.value = TRUE, B = B)$p.value
  }

@@

  list(statistics = stat, p.value = p.value, 
       estimate = c(mean = mu, sd = sigma),
       stat.sim = stat.b)
}

@@

@@

test_block <- function(ar, B = 1000, l, n) {

  x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n)
  stat <- ks.test(x, "pnorm")$statistic
  stat.b <- double(B)
  for (i in 1:B) {
    x.b <- x[nmblk(n, l)]
    stat.b[i] <- ks.test(x.b, "pnorm")$statistic
  }

  p.value <- (sum(stat.b >= stat)) / (B + 1)
  list(p.value = p.value)
}

# Naive KS-test to show consequence of fitted parameters
test_naive_block <- function(ar, n) {
  x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n)
  p.value <- ks.test(x, "pnorm")$p.value
  list(p.value = p.value)
}

# Generate results
pvals_block <- suppressWarnings(replicate(20, test_block(ar = 0.5, B = 1000, l = 5, n = 100)$p.value))
pvals_block
pvals_naive_block <- suppressWarnings(replicate(20, test_naive_block(ar = 0.5, n = 100)$p.value))

# Create a master data_frame with all the results
histogram <- c(rep("Block", 20), rep("Naive", 20))
p_values <- c(pvals_block, pvals_naive_block)
results <- data_frame(p_values, histogram)

# Generate histograms plot
hist_boot <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~histogram, scales = "free_y")
hist_boot
```

```{r}
# Split sample size into blocks, apply bootstrap onto blocks. Use that as x.b. Fit, stat.b
# Test parametric bootstrap as a solution to fitting parameters
test_corr_block <- function(ar, B = 1000, l, n) {

@@

```{r}
ggsave(filename="hist_normal.pdf", plot=hist_normal, path = "/Users/anthony/KS-Test-Thesis/Manuscript")
ggsave(filename="hist_rounded.pdf", plot=hist_rounded, path = "/Users/anthony//KS-Test-Thesis/Manuscript")
ggsave(filename="hist_correlation.pdf", plot=hist_correlation, path = "/Users/anthony/KS-Test-Thesis/Manuscript")
ggsave(filename="hist_dgof.pdf", plot=hist_dgof, path = "/Users/anthony/KS-Test-Thesis/Manuscript")
ggsave(filename="hist_dgofsim.pdf", plot=hist_dgofsim, path = "/Users/anthony/KS-Test-Thesis/Manuscript")
ggsave(filename="hist_parametric.pdf", plot=hist_parametric, path = "/Users/anthony/KS-Test-Thesis/Manuscript")
```

>>>>

@@

  list(p.value = p.value)
}

@@

```{r}
noisy <- function(x) {
  v <- var(x)
  n <- length(x)
  noise <- rnorm(n, mean = 0, sd = 1/100*v)
  return(x + noise)
}

ar <- 0.5
n <- 10
x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n)
x
noisy(x)
```

@@

test_block <- function(x, B = 1000, l) {

  stat <- ks.test(x, "pnorm")$statistic

  n <- length(x)
  stat.b <- double(B)
  for (i in 1:B) {
    x.b <- noisy(x[mvblk(n, l)])
    # add small noise compared to variance of x. sd of noise is 1%, or 1/10%, of sd of regular variance
    stat.b[i] <- ks.test(x.b, "pnorm")$statistic
  }
  p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
  list(p.value = p.value)

}

test_naive_block <- function(ar, n) {
  x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n)
  p.value <- ks.test(x, "pnorm")$p.value
  list(p.value = p.value)
}

ptm <- proc.time()

ar = 0.5
n = 100
n_tests = 1000
l = 10
pvals_boot <- replicate(n_tests, test_block(arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n), B = 1000, l = l)$p.value)
pvals_naive_block <- replicate(n_tests, test_naive_block(ar = ar, n = n)$p.value)

# Create a master data_frame with all the results
histogram <- c(rep("Boot", n_tests), rep("Naive", n_tests))
p_values <- c(pvals_boot, pvals_naive_block)
results <- data_frame(p_values, histogram)

# Generate histograms plot
hist_boot <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~histogram, scales = "free_y")
hist_boot

proc.time() - ptm
```

```{r}
blkboot <- function(tseries, statistic, R, l) {
  n <- length(tseries)

  stat <- statistic(tseries)

  nm.stat <- replicate(R, statistic(noisy(tseries[nmblk(n, l)])))
  mv.stat <- replicate(R, statistic(noisy(tseries[mvblk(n, l)])))

  nmp.value <- (sum(nm.stat >= stat) + 0.5) / (R + 1)
  mvp.value <- (sum(mv.stat >= stat) + 0.5) / (R + 1)

  list(stat = stat, nmp.value = nmp.value, mvp.value = mvp.value)
}

ar1 <- function(x) ks.test(x, "pnorm")$statistic

do1rep <- function(n, ar, l) {
  x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n)
  bt <- blkboot(x, ar1, R = 1000, l)
  list(stat = bt$stat, nmp.value = bt$nmp.value, mvp.value = bt$mvp.value)
}

ptm <- proc.time()

n <- 100
ar <- 0.5
l = 5
n_tests <- 1000

pvals_boot2 <- replicate(n_tests, do1rep(n, ar, l)$mvp.value)
pvals_naive_block <- replicate(n_tests, test_naive_block(ar = ar, n = n)$p.value)

# Create a master data_frame with all the results
histogram <- c(rep("Boot", n_tests), rep("Naive", n_tests))
p_values <- c(pvals_boot2, pvals_naive_block)
results <- data_frame(p_values, histogram)

# Generate histograms plot
hist_boot2 <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~histogram, scales = "free_y")
hist_boot2

proc.time() - ptm
```
```{r}
 # Split sample size into blocks, apply bootstrap onto blocks. Use that as x.b. Fit, stat.b
 # Test parametric bootstrap as a solution to fitting parameters
test_corr_block <- function(ar, B = 1000, l, n) {

@@

```{r}
library(boot)

fun <- function(x) {
  x <- noisy(x)
  p.value <- ks.test(x, "pnorm")$p.value
  return(p.value)
}

test <- replicate(25, tsboot(arima.sim(list(ar = 0.5), rand.gen = rnorm, sd = sqrt(1-0.5^2), 100), fun, 1000, sim = "fixed", l = 5))
hist(test[,1]$t)
```

# Create the histograms displaying p-values from each test
hist1 <- suppressWarnings(test_rounded(1000, 100, 2))
hist2 <- suppressWarnings(test_rounded(1000, 100, 1))

# Create a master data_frame with all the results
histogram <- c(rep(".01", 1000), rep(".1", 1000))
p_values <- c(hist1, hist2)
results <- data_frame(p_values, histogram)

# Generate histograms plot
hist_rounded <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~histogram, scales = "free_y")
```

```{r}
# Test the KSgeneral package as a solution to rounded data
test_general <- function(n_tests, n_samples, digits, B = 100) {

  results1 <- c()
  results2 <- c()

    # Generate random rounded data, perform 3 KS-tests, and store the p-values
    # 1. Using the rounded normal step function
    # 2. Using the naive continuous standard normal function
    data <- round(rnorm(n_samples), digits)
    results1[i] <- KSgeneral::disc_ks_test(data, sfun, exact = TRUE)$p.value
    results2[i] <- dgof::ks.test(data, "pnorm")$p.value

  }

  # Create a master data_frame for p-values
  test <- c(rep("KSgeneral", n_tests), rep("Naive", n_tests))
  digits <- c(rep(.1^digits, 2*n_tests))
  p_values <- c(results1, results2)
  results <- data_frame(p_values, test, digits)

# Create the histograms displaying p-values from each test
test1 <- suppressWarnings(test_general(1000, 100, 2))
test2 <- suppressWarnings(test_general(1000, 100, 1))
results <- rbind(test1, test2)

# Generate histograms plot
hist_general <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~test+digits, ncol = 2, scales = "free_y")
hist_general
```

  results1 <- c()
  results2 <- c()

    # Generate random rounded data, perform 3 KS-tests, and store the p-values
    # 1. Using the rounded normal step function
    # 2. Using the naive continuous standard normal function
    data <- round(rnorm(n_samples), digits)
    results1[i] <- ks.test(data, sfun)$p.value
    results2[i] <- ks.test(data, "pnorm")$p.value

  }

# Create the histograms displaying p-values from each test
test1 <- suppressWarnings(test_dgof(1000, 100, 2))
test2 <- suppressWarnings(test_dgof(1000, 100, 1))
results <- rbind(test1, test2)

# Generate histograms plot
hist_dgof <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~test+digits, ncol = 2, scales = "free_y")
```

  for (i in 1:n_tests) {
    cat(i, "\n")
    # Generate random rounded data, perform 2 KS-tests, and store the p-values
    # 1. Using the rounded normal step function
    # 2. Using the rounded normal step function with simulated p-values
    test <- round(rnorm(n_samples), digits)
    results1[i] <- ks.test(test, sfun)$p.value
    results2[i] <- ks.test(test, sfun, simulate.p.value = TRUE, B = B)$p.value
  }

      # Generate random correlated data, perform a KS-test, and store the p-value
      data <- arima.sim(model = list(ar = ars[i]), rand.gen = rnorm, sd = sqrt(1-ars[i]^2), n = 100)
      ar_results <- add_row(ar_results, p_value = ks.test(data, "pnorm")$p.value, ar = round(ars[i], 1))
    }
  }

 # Set AR coefficients and generate results
ars <- seq(-0.3, 0.3, by = 0.1)
ar_results <- test_correlation(1000, ars)

# Generate histograms plot
hist_correlation <- ggplot(ar_results, aes(x = p_value)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~ar, scales = "free_y", ncol = 4)
```

```{r}
ggsave(filename="hist_parametric.pdf", plot=hist_parametric, path = "../Manuscript", width = 4, height = 2, units = "in")
ggsave(filename="hist_rounded.pdf", plot=hist_rounded, path = "../Manuscript", width = 4, height = 2, units = "in")
ggsave(filename="hist_dgof.pdf", plot=hist_dgof, path = "../Manuscript", width = 4, height = 4, units = "in")
ggsave(filename="hist_dgofsim.pdf", plot=hist_dgofsim, path = "../Manuscript", width = 4, height = 4, units = "in")
ggsave(filename="hist_correlation.pdf", plot=hist_correlation, path = "../Manuscript", width = 8, height = 4, units = "in")
```
